Distributional Trees and Forests

### 2017-10-05 pkg/disttree/inst/draft/draft.Rnw
started description of rain data set
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@1624 255f4249-2263-4417-b1ea-8498779e27a7

\newpage
\section{Rain}
In this section precipation data of 30 years is analyzed. The response variable is the meassured total precipiation within 24 hours of each day in July at the station ... .\\
The following methods are applied on this data set:
\begin{itemize}
\item distributional tree
\item distributional forest
\item gamlss
\item gamboostLSS
\item EMOS
\end{itemize}

>>>>

\newpage
\section{Rain}
In this section precipation data of 30 years is analyzed. The response variable is the meassured total precipiation within 24 hours of each day in July at the station ... .\\

\begin{tabular}{| l | c |}
\hline
basic covariates & variations
\hline
tppow: total precipitation power transformed & tppow_mean, tppow_spread, tppow_min, tppow_max \\
& tppow_0612, tppow_1218, tppow_1824, tppow_2430 \\
\hline
capepow:    & capepow_mean, capepow_spread, capepow_min, capepow_max \\
& capepow_0612, capepow_1218, capepow_1824, capepow_2430 \\
\hline
tcloc: total cloud coverage & \\
\hline
\hline
\end{table}

The following methods are applied on this data set:

\begin{tabular}{| l | c  c  c  c |}
\hline
model & mu link & sigma link & mu covariates & sigma covariates \\
\hline
disttree & identity & log & all covariates & all covariates \\ 
\hline
distforest & identity & log & all covariates & all covariates \\
\hline
gamlss & identity & log & manually selected covariates: & manually selected covariates \\
\hline
gamboostLSS & identity & log & all covariates & all covariates \\
\hline
EMOS & identity & log & tppow_mean & tppow_spread \\
\hline
\end{table}
